\section{The simply-typed lambda calculus}\label{sec:stlc}
\begin{figure}
\begin{singlespace}
\begin{minipage}{.46\textwidth}
	\begin{center}Church-style\end{center}
\def\baselinestretch{0}
\small
\begin{align*}
\textbf{term syntax} \\
t,s ::= &~ x           & \text{variable}    \\
      | &~ \l(x:A) . t & \text{abstraction} \\
      | &~ t ~ s       & \text{application} \\
\\
\textbf{type syntax} \\
A,B ::= &~ A -> B  & \text{arrow type} \\
      | &~ \iota   & \text{ground type}   \\
\end{align*}
\[ \textbf{typing context} \]\vspace*{-1em}
\begin{align*}\quad
\Gamma ::= &~ \cdot \\
	 | &~ \Gamma, x:A \quad (x\notin \dom(\Gamma)) \\
\end{align*}
\[ \textbf{typing rules}
	\qquad \framebox{$\Gamma |- t : A$} \]
\vspace*{-1em}
\begin{align*}
& \inference[\sc Var]{x:A \in \Gamma}{\Gamma |- x:A} \\
& \inference[\sc Abs]{\Gamma,x:A |- t : B}
		     {\Gamma |- \l(x:A).t : A -> B} \\
& \inference[\sc App]{\Gamma |- t : A -> B & \Gamma |- s : A}
		     {\Gamma |- t~s : B} \\
\end{align*}
\[ \textbf{reduction rules}
	\quad \framebox{$t --> t'$} \]
\vspace*{-1em}
\begin{align*}
& \inference[\sc RedBeta]{}{(\l(x:A).t)~s --> t[s/x]} \\
& \inference[\sc RedAbs]{t --> t'}{\l(x:A).t --> \l(x:A).t'} \\
& \inference[\sc RedApp1]{t --> t'}{t~s --> t'~s} \\
& \inference[\sc RedApp2]{s --> s'}{t~s --> t~s'} \\
\end{align*}
\end{minipage}
\begin{minipage}{.46\textwidth}
	\begin{center}Curry-style\end{center}
\def\baselinestretch{0}
\small
\begin{align*}
\textbf{term syntax} \\
t,s ::= &~ x           \\
      | &~ \l x    . t \\
      | &~ t ~ s       \\
\\
\textbf{type syntax} \\
A,B ::= &~ A -> B \\
      | &~ \iota  \\
\end{align*}
\[ \textbf{typing context} \]\vspace*{-1em}
\begin{align*}\quad
\Gamma ::= &~ \cdot \\
	 | &~ \Gamma, x:A \quad (x\notin \dom(\Gamma)) \\
\end{align*}
\[ \textbf{typing rules}
	\qquad \framebox{$\Gamma |- t : A$} \]
\vspace*{-1em}
\begin{align*}
& \inference[\sc Var]{x:A \in \Gamma}{\Gamma |- x:A} \\
& \inference[\sc Abs]{\Gamma,x:A |- t : B}
		     {\Gamma |- \l x   .t : A -> B} \\
& \inference[\sc App]{\Gamma |- t : A -> B & \Gamma |- s : A}
		     {\Gamma |- t~s : B} \\
\end{align*}
\[ \textbf{reduction rules}
	\quad \framebox{$t --> t'$} \]
\vspace*{-1em}
\begin{align*}
& \inference[\sc RedBeta]{}{(\l x   .t)~s --> t[s/x]} \\
& \inference[\sc RedAbs]{t --> t'}{\l x   .t --> \l x   .t'} \\
& \inference[\sc RedApp1]{t --> t'}{t~s --> t'~s} \\
& \inference[\sc RedApp2]{s --> s'}{t~s --> t~s'} \\
\end{align*}
\end{minipage}
~\\
\caption{Simply-typed lambda calculus in Church style and Curry style}
\label{fig:stlc}
\end{singlespace}
\end{figure}
We illustrate two styles of the simply-typed lambda calculus (STLC)
in Figure \ref{fig:stlc}. The left column of the figure describes
the Church-style STLC and the right column describes the Curry-style STLC.

A term can be either a variable, an abstraction (\aka\ lambda term), or
an application. The distinction between the two style comes from whether
the abstraction has type annotation in the term syntax. Abstractions in
Church style have the form $\lambda(x:A).t$ with type annotation $A$ on
the variable $x$ bound in $t$. Abstractions in Curry style have the form
$\lambda x.t$ without any type annotation. The differences in typing rules
and reduction rules between the two styles follow from this distinction
in the term syntax.

A type can be either an arrow type or a ground type.
The type syntax is exactly the same in both styles.
There should be no questions regarding arrow types as they are types for
functions. For instance, abstractions have arrow types. We need some
ground types in order to populate the types, as a base case for
the inductive definition of types. Otherwise, if there were no ground types,
we would not have any types\footnote{If we allow infinite types, then it is
	possible to populate types without ground types. There exist exotic
	lambda calculi with infinite types, but rather uncommon.}
%% Then, such version of STLC will be very uninteresting since there cannot
%% be any well-typed terms because there are no types to begin with.
Here, I choose to include only the most simple ground type $\iota$,
which also known as the void type. Note that there exist any closed term of
type $\iota$. The only way to construct terms of type $\iota$ is when we
have a bound variable known to have type $\iota$ in the typing context.
Having just the void type as a ground type is enough for my purpose of
motivating the discussions for the polymorphic type systems, without
complicating the term syntax of the STLC.

When people use STLC to model a programming language (with simple types),
they usually provide richer set of ground types other than the void type
(\eg, unit, boolean, natural numbers). In such versions of STLC, whose
type syntax is extended with richer set of ground types, they also need to
extend the term syntax by providing normal terms (or, constants) for
those ground types (\eg, \textsf{true} and \textsf{false} for booleans) and
eliminators (\eg, if-then-else expression for booleans) that can examine
the normal terms. Later on, we shall see that polymorphic type systems
such as System \F\ (\S\ref{sec:f}) and \Fw (\S\ref{sec:fw}) are expressive
enough to encode those ground types without introducing them as primitive
constructs of the calculi.

Typing rules are the rules to derive (or prove) typing judgments.
A typing judgment $\Gamma |- t : A$ means that the term $t$ has type $A$
under the typing context $\Gamma$. We say $t$ is well-typed
(or, $t$ is a well-typed term) under $\Gamma$ when we can derive (or prove)
a typing judgment $\Gamma |- t : A$ for some $A$ according to the typing rules.
There are three typing rules --
one typing rule for each item of the term syntax.
Therefore, the typing rules of the STLC are syntax directed in both styles.
That is, there is always only one rule to choose for the typing derivation
by examining the shape of the term.
 
The reduction rules in Figure \ref{fig:stlc} describes the $\beta$-reduction
for the STLC. The \rulename{RedBeta} rule describes the key concept
the $\beta$-reduction on the $\beta$-redex. A $\beta$-redex is an application
of an abstraction to another term. The other three rules describe the idea
that a redex may appear in subterms although the term itself is not a redex.
The reduction rules of the STLC are virtually the same as the reduction rules
of the $\beta$-reduction the untyped lambda calculus. Note that reduction rules
are not deterministic. There is no preferred order when there are more than one
redex in a term. For instance, when there are redexes in both $t$ and $s$
in the application $t s$, one may apply any of the two rules \rulename{RedApp1}
and \rulename{RedApp2}.

\paragraph{}
We first discuss two important properties of the STLC
(subject reduction and strong normalization), which hold
in both Curry style and Church style (\S\ref{sec:stlc:srsn}).
Then, we discuss distinctive characteristics of each style
(\S\ref{sec:stlc:church},\S\ref{sec:stlc:curry}).
Finally, we motivate the discussion of polymorphic type systems
by reviewing the limitations of the STLC (\S\ref{sec:stlc:topoly}).

\subsection{Subject reduction and strong normalization}\label{sec:stlc:srsn}
We discuss two important properties of the STLC, which holds in both
Church style and Curry style -- \emph{subject reduction} (\aka\
\emph{type preservation}) and \emph{strong normalization}.

\paragraph{Subject reduction} is a property that reduction preserves type,
as stated below:
\begin{theorem}[subject reduction]
	$\inference{\Gamma |- t : A  & t --> t'}{\Gamma |- t' : A}$
\end{theorem}
That is, when a well-typed term takes a reduction step, then the reduce term
also has the same type. We can prove subject reduction (\aka\ type preservation)
by induction on the derivation of the reduction rules.
The only interesting case is the \rulename{RedBeta} rule. Proof for all
the other rules are simply done by applying the induction hypothesis.
Proof for the \rulename{RedBeta} rule amounts to proving the substitution lemma:
\begin{lemma}[substitution]
$ \inference{\Gamma,x:A |- t : B  & \Gamma |- s : A}{\Gamma |- t[s/x] : B} $
\end{lemma}
Proof of the substitution lemma is a straightforward induction on
the derivation of the typing judgement.

When people use STLC to model a programming language,
they usually consider another property called \emph{progress},
which states that well-typed terms are either values or
able to take an evaluation step. An evaluation is a reduction strategy
(\ie, certain subset of the reduction relation), which is often deterministic.
Values are terms that meet certain syntactic criteria, which is intended not
to take further evaluation steps. In such a setting, type safety means
subject reduction together with progress. However, in a calculus considering
reductions to normal terms, rather than evaluations to values, type safety is
no more than subject reduction since normal terms are irreducible by definition.

\paragraph{Strong normalization} is another important property of the STLC,
when we intend to consider terms of the STLC as a proof of a propositional logic
by the Curry-Howard correspondence. The proof strategy we present here is
to define the set of strongly normalizing terms, which may or may not be
well typed, and show that all well-typed terms belong to this set.
We shall continue the discussion on strong normalization using
the Curry-style term syntax, but this proof strategy also works well
for the Church-style STLC\footnote{This proof strategy generalizes well
	to more complicated systems such as System \F, System \Fw, and
	even for dependently-typed calculi, such as
	the Calculus of Constructions\cite{Geuvers94}.}.
In fact, this strategy originates from Girard's strong normalization proof
for System \F\ using reducibility candidates \cite{Gir71}, and later rephrased
using Tait's saturated sets \cite{Tait75}. In particular, I adopt
the notations from the work of \citet{AbeMat04}, which includes
a strong normalization proof for an extension of \Fw\ using saturated sets.
The strong normalization proofs for System \F\ (\S\ref{sec:f}) and
\Fw\ (\S\ref{sec:fw}) in this chapter, and also for System \Fi\
(Chapter \ref{ch:fi}) and \Fixi\ (Chapter \ref{ch:fixi}) in later chapters,
are also based on the same strategy using saturated sets, with gradually
increasing complexity for the interpretation of types in each of those systems.

A straightforward inductive definition of $\SN$,
the set of strongly normalizing terms, would be:
\[
\inference{s_1,\ldots,s_n\in\SN}{x~s_1~\cdots~s_n \in \SN}
\qquad
\inference{t \in \SN}{\l x.t \in \SN}
\qquad
\inference{t' \in \SN & t --> t'}{t \in \SN}
\]
That is, variables and applications of a variable to a strongly normalizing term
are in $\SN$, abstractions are in $\SN$ when their bodies are in $\SN$,
and terms that reduce to $\SN$ are also in $\SN$. Relying on the fact that
normal order reduction (\ie, reduce the outermost leftmost redex first) always
leads to a normal form if a normal form exists, we can alter the last rule of
the inductive definition above more syntactically, yet defining the same set
$\SN$, as follows:
\[
\inference{s_1,\ldots,s_n\in\SN}{x~s_1~\cdots~s_n \in \SN}
\quad
\inference{t \in \SN}{\l x.t \in \SN}
\quad
\inference{t[s/x]~s_1~\cdots~s_n\in \SN & s\in\SN}
	{(\lambda x.t)~s~s_1~\cdots~s_n \in \SN}
\]

A set $\mathcal{A}$ is saturated when it is closed under adding
strongly normalizing neutral terms and strongly normalizing weak head expansion:
\[
\inference{s_1,\ldots,s_n\in\SN}{x~s_1~\cdots~s_n \in \mathcal{A}}
\qquad\qquad\qquad\qquad\quad
\inference{t[s/x]~s_1~\cdots~s_n\in \mathcal{A} & s\in\SN}
	  {(\l x.t)~s~s_1~\cdots~s_n \in \mathcal{A}}
\]
We can easily observe that $\SN$ is a saturated set by definition
since we can get the first and last part of the inductive definition for $\SN$
when $\mathcal{A}=\SN$. We can define an arrow operator over saturated sets
(or, saturated-set arrow) as follows:
\[ \mathcal{A} -> \mathcal{B} = \{ t \in \SN \mid t~s \in \mathcal{B} ~\text{for all}~ s \in \mathcal{A} \} \]
It is known that $\mathcal{A} -> \mathcal{B}$ is saturated
when both $\mathcal{A}$ and $\mathcal{B}$ are saturated.

\begin{figure}
\begin{singlespace}
\begin{description}
\item[Interpretation of types] as saturated sets of normalizing terms:
\begin{align*}
[| \iota  |] &= \bot \qquad\qquad (\text{the minimal saturated set}) \\
[| A -> B |] &= [| A |] -> [| B |]
\end{align*}

\item[Interpretation of typing contexts] as sets of valuations ($\rho$):
\[ [| \Gamma |] =
	\{\; \rho\,\in\,\dom(\Gamma) -> \SN ~\mid~
             \rho(x) \in [|\Gamma(x)|] ~\text{for all}~x\in\dom(\Gamma) \;\}
\]

\item[Interpretation of terms] as terms themselves whose free variables are
	substituted according to the given valuation ($\rho$):
\begin{align*}
[|x|]_\rho      &= \rho(x) \\
[|\l x.t|]_\rho &= \l x.[|t|]_\rho  \qquad (x\notin\dom(\rho)) \\
[|t~s|]_\rho    &= [|t|]_\rho~[|s|]_\rho
\end{align*}
\end{description}
\caption[Interpretation of STLC for proving strong normalization]
	{Interpretation of types, typing contexts, and terms of STLC
         for the proof of strong normalization}
\label{fig:interpSTLC}
\end{singlespace}
\vspace*{.5em}\hrule
\end{figure}

We interpret types as saturated subsets (\ie, subsets that are saturated) of
$\SN$ as in Figure \ref{fig:interpSTLC}. We interpret the void type as
the minimal saturated set ($\bot$), which is saturated from the empty set.
We choose the symbol $\bot$ since saturated sets form a complete lattice
under the subset relation as the partial order. We may denote $\SN$ as $\top$
since it is the maximal element of the lattice. Note that $\bot$,
or $[|\iota|]$, does not include any abstraction since $\iota$ is
not a type of a function. Arrow types ($A -> B$) are interpreted as
the saturated-set arrow over the interpretations of the domain type
and the range type ($[|A|] -> [|B|]$).

We interpret a typing context ($\Gamma$) as a set of valuations ($\rho$).
For every variable binding in the typing context ($x:A \in \Gamma$),
a valuation should map the variable ($x$) to a term that belongs to
the interpretation of its desried type ($[|A|]$). That is, if
$x : A \in \Gamma$ then any $\rho \in [|\Gamma|]$ should satisfy
that $\rho(x) \in [|A|]$.

The Proof of strong normalization amounts to proving the following theorem:
\begin{theorem}[soundness of typing]
$ \inference{\Gamma|- t:A & \rho \in [|\Gamma|]}{[|t|]_\rho \in [|A|]} $
\end{theorem}
\begin{proof}
We prove by induction on the typing derivation ($\Gamma|- t:A$).
\paragraph{}
For variables, it is trivial to show that
$ \inference{\Gamma |- x:A & \rho \in [|\Gamma|]}{[|x|]_\rho \in [|A|]} $.

Due to the \rulename{Var} rule, we know that $x:A \in \Gamma$.
So, $[|x|]_\rho =\rho(x)\in[|\Gamma(x)|] = [|A|]$.

\paragraph{}
For abstractions, we need to show that
$ \inference{\Gamma |- \l x.t : A -> B & \rho \in [|\Gamma|]}
	     {[|\l x.t|]_\rho \in [|A -> B|]} $.

Since $[|\l x.t|]_\rho = \l x.[|t|]_\rho$ and
$[|A -> B|] = \{ t\in \SN \mid t~s\in[|B|]~\text{for all}~s\in[|A|] \}$,
what we need to show is equivalent to the following:
\[ \inference{\Gamma |- \l x.t : A -> B & \rho \in [|\Gamma|]}
	     {\l x.[|t|]_\rho \in
		\{ t\in \SN \mid t~s\in[|B|] ~\text{for all}~ s\in[|A|] \} }
\]
By induction, we know that:
$ \inference{\Gamma,x:A |- t : B & \rho' \in [|\Gamma,x:A|]}
	     {[|t|]_{\rho'} \in [|B|]} $.

Since this holds for all $\rho' \in [|\Gamma,x:A|]$, it also holds
for particular $\rho' = \rho[x \mapsto s]$ for any $s \in [|A|]$.
So, $[|t|]_{\rho[x\mapsto s]} = ([|t|]_\rho)[s/x]\in[|B|]$ for any $s\in[|A|]$.
Since saturated sets are closed under normalizing weak head expansion,
$(\l x.[|t|]_\rho)~s \in[|B|]$ for any $s\in[|A|]$.
Therefore, $\l x.[|t|]_\rho$ is obviously in the very set,
which we wanted it to be in (\ie,
$\l x.[|t|]_\rho\in\{t\in \SN \mid t~s\in[|B|] ~\text{for all}~ s\in[|A|]\}$).

\paragraph{}
For applications, we need to show that
$ \inference{\Gamma |- t~s : B & \rho\in[|\Gamma|]}{[|t~s|]_\rho \in [|B|]} $.

By induction we know that
$
\inference{\Gamma |- t : A -> B & \rho\in[|\Gamma|]}{[|t|]_\rho \in [|A -> B|]}
\qquad
\inference{\Gamma |- s : A & \rho\in[|\Gamma|]}{[|s|]_\rho \in [|A|]}
$.

Then, it is straightforward to see that $[|t~s|]_\rho\in[|B|]$
by definition of $[|A -> B|]$.\\
\end{proof}

\begin{corollary}[strong normalization]
	$\inference{\Gamma |- t : A}{t \in \SN}$
\end{corollary}
Once we have proved the soundness of typing with respect to interpretation,
it is easy to see that STLC is strongly normalizing by giving a trivial
interpretation such that $\rho(x) = x$ for all $x\in\dom(\Gamma)$. Note that
$[|t|]_\rho = t \in [|A|] \subset \SN$ under the trivial interpretation.



\subsection{Characteristics of the Church-style STLC}\label{sec:stlc:church}
In Church style, the variable ($x$) in an abstraction
($\l(x:A).t$) has a type annotation ($A$). Intuitively, we may think of
the abstraction ($\l(x:A).t$) as a function that expects an argument of
the type ($A$) specified by the type annotation.

There are some interesting properties that hold in Church style,
but not in Curry style. Here, we discuss two of them:
\begin{itemize}
\item \emph{Uniqueness of typing}
$\qquad\inference{\Gamma |- t : A & \Gamma |- t : A'}{A = A'} $

\item \emph{Type equivalence between well-typed $\beta$-equivalent terms}
\begin{align*}
& \inference{t =_{\beta} t' & \Gamma |- t : A & \Gamma |- t' : A'}{A = A'} \\
& \text{where $=_{\beta}$ is the reflexive symmetric transitive closure of $-->$.}
\end{align*}
\end{itemize}

\emph{Uniqueness of typing}, described in the first item above,
holds in the Church-style STLC.  More specifically, given
a well-formed typing context $\Gamma$ and a term $t$ as input,
if the term is well typed, that is, $\Gamma |- t : A$ for some type $A$,
then that $A$ is the unique such type. We can prove this by induction on
the derivation of the typing judgment.
For variables, it trivially holds since the variables appearing in
the typing contexts are unique.
For abstractions, we use induction on the derivation.
To use the induction hypothesis we should make sure that
the typing context ($\Gamma,x:A$) and the term $t$ of the premise
is uniquely determined. It is easy to see that they are uniquely determined
since all the peaces appearing in the input (\ie, the typing context and
the term) of the premise (in particular, $\Gamma$, $A$, and $t$) are
part of the input (in particular the term $\l(x:A).t$) of the conclusion.
Therefore, by induction hypothesis, $B$ is uniquely determined, and,
as a consequence, $A -> B$ is uniquely determined.
For applications, it is easy to show by induction for each of the premise.
This proof describes the essence of the type reconstruction algorithm for
the Church-style STLC.


Proving \emph{type equivalence between well-typed $\beta$-equivalent terms},
described in the second item above, amounts to proving \emph{type equivalence
between terms before and after well-typed $\beta$-reducion
(or, $\beta$-expanion)},
described below:
\begin{align}
\inference{t --> t' & \Gamma |- t : A & \Gamma |- t' : A'}{A = A'}
	\label{eqn:welltypedarrow}
\end{align}
That is, when a well-typed term ($t$) reduces to
another well-typed term ($t'$) in single step ($t --> t'$),
the types of those two terms are identical ($A=A'$).
Since the claim above is symmetric, we can also say: when a well-typed term
($t'$) expands to another well-typed term ($t$) in single step ($t' <-- t$),
the types of those two terms are identical ($A'=A$).
Let us break down the claim (\ref{eqn:welltypedarrow}) above into two parts:
\[
\inference{t --> t' & \Gamma |- t : A}
          {\Gamma |- t' : A' ~~\text{implies}\quad A = A'} \qquad
	\begin{smallmatrix}
		\text{type equivalence between terms} \\
  		\text{before and after well-typed $\beta$-reduction}
	\end{smallmatrix}
\]
\[
\inference{t --> t' & \Gamma |- t' : A'}
          {\Gamma |- t : A \quad\text{implies}\quad A = A'} \qquad
	\begin{smallmatrix}
		\text{type equivalence between terms} \\
  		\text{before and after well-typed $\beta$-expansion}
	\end{smallmatrix}
\]~\vspace*{-3em}\\

We know that the former (type equivalence between terms before and after
well-typed $\beta$-reduction) holds because we already know of
a stronger property, subject reduction, which we discussed earlier
(repeated below) that it is one of the properties that commonly hold
in both Church style and Curry style.
\begin{align*}
\inference{\Gamma |- t : A  & t --> t'}{\Gamma |- t' : A}
 &\qquad \text{subject reduction, or type preservation}
\end{align*}

\begin{figure}
\begin{singlespace}
\begin{tabular}{lp{7cm}}
$t <-- (\l(x:\iota).x)~t$ &
relying on the property of the void type
that $\iota$ is not inhabited by any term
\\ ~ \\
$t <-- (\l(x:\iota -> \iota).t)~(\l(x:\iota).x~x)$ &
without relying on the property of $\iota$ : \par
apply a constant function to an already ill-typed term (self application)
\end{tabular}
\end{singlespace}
\caption{Examples of $\beta$-expansions to ill-typed terms}
\label{ill-typed_expand}
\hrule
\end{figure}

So, what is interesting about the Church style STLC, in contrast to
the Curry-style STLC, is the latter part of the claim that terms before and
after well-typed $\beta$-expansion must always be of same type. Unlike
the former part of the claim on $\beta$-reduction, where reduced term
is always well-typed (corollary of subject reduction), we really need
the condition that expanded term is well-typed ($\Gamma |- t : A$).
This is because a well-typed term can be expanded to a ill-typed term.
In fact, we can always expand any well-typed term to ill-typed terms
(see Figure \ref{ill-typed_expand}).

The proof of the claim (\ref{eqn:welltypedarrow}) is very simple.
Recall that we want to show that $A = A'$,
assuming $t --> t'$, $\Gamma |- t : A$ and $\Gamma |- t' : A'$.
We can prove it by using \emph{subject reduction} and
\emph{uniqueness of typing} as follows:
\[ \inference[(\emph{uniqueness of typing})]
	{ \inference[(\emph{subject reduction})\!\!\!]
		{t --> t' & \Gamma |- t : A}
		{\Gamma |- t' : A \phantom{a_f}} 
	& \Gamma |- t' : A' }
	{ A = A' }
\]

\subsection{Characteristics of the Curry-style STLC}\label{sec:stlc:curry}
In Curry style, there is no annotation on the variable in an abstraction.
Since the variable binding in the abstraction is no longer fixed to
a specific type, \emph{uniqueness of typing} does not hold,
unlike in Church style. For instance, the identity function ($\l x.x$)
could have one of any type that has of the form $A -> A$, such as:
\begin{quote}\vspace*{-1em}
\begin{singlespace}
$\Gamma |- \l x.x : \iota -> \iota$ \\
$\Gamma |- \l x.x : (\iota -> \iota) -> (\iota -> \iota)$ \\
$\Gamma |- \l x.x : (\iota -> (\iota -> \iota)) -> (\iota -> (\iota -> \iota))$ \\
$\Gamma |- \l x.x : ((\iota -> \iota) -> \iota) -> ((\iota -> \iota) -> \iota)$ \\
$\Gamma |- \l x.x : ((\iota -> \iota) -> (\iota -> \iota)) -> ((\iota -> \iota) -> (\iota -> \iota))$ \\
$~~~~ \vdots $
\end{singlespace}
\end{quote}
So, we read the typing judgment $\Gamma |- t : A$ in Curry style as
\begin{quote}
$t$ \emph{can have type} $A$ under the typing context $\Gamma$,
\end{quote}
unlike in Church style where we read the typing judgment as
\begin{quote}
$t$ \emph{has the type} $A$ under the typing context $\Gamma$.
\end{quote}
However, we do not consider the Curry-style STLC to be
a polymorphic type system since the typing for a variable
under a well-formed context is still unique. That is,
\[ \inference{\Gamma |- x : A & \Gamma |- x : A'}{A = A'} \]

Type equivalence between terms before and after well-typed $\beta$-reduction
(or $\beta$-expansion) does not hold either, unlike in Church style.
This is expected since uniqueness of typing does not hold in Curry style.
Even when a well-typed term reduces to another well-typed term, they may be
given different types.\footnote{Subject reduction still holds for
the Curry-style STLC since we can choose to give the same type to
the reduced term as the type before the reduction.}
Consider the reduction $(\l x'.x')(\l x.x) --> \l x.x$.
We can give different types to the term before the reduction and the
term after the reduction. For example,
\[\setpremisesend{.1em} 
\inference[\sc App]
 {
   \inference[\sc Lam]
     { \inference[\sc Var]
         {x' : \iota -> \iota ~\in~ \cdot, x' : \iota -> \iota}
         {\cdot,x' : \iota -> \iota |- x': \iota -> \iota}
     }
     {\cdot |- \l x'.x' : (\iota -> \iota) -> (\iota -> \iota)}
 &
   \inference[\sc Lam]
     {\inference[\sc Var]{x:\iota ~\in~ \cdot,x:\iota}
                         {\cdot,x:\iota |- x:\iota} \phantom{x'}}
     {\cdot |- \l x.x : \iota -> \iota \phantom{(x')}}
 }
 {\cdot |- (\l x'.x')(\l x.x) : \iota -> \iota}
\]
\[\qquad\qquad\qquad\quad
\inference[\sc Lam]
  {\inference[\sc Var]{x:\iota->\iota ~\in~ \cdot,x:\iota->\iota}
                      {\cdot,x:\iota->\iota |- x:\iota->\iota} }
  {\cdot |- \l x.x : (\iota -> \iota) -> (\iota -> \iota)}
\]

%% does the set of possible types get larger after reduction even when
%% the only ground type is the void type? I am not sure. So, I won't
%% elaborate on this.

\paragraph{}
\KYA{TODO there should be a story on type inference and principal types
	to motivate the HM type system}

\subsection{Motivations for polymorphic type systems}\label{sec:stlc:topoly}
TODO
